Retrofitting Effect Handlers onto OCaml

### 2021-03-24 retro-concurrency.tex
updates

%\vspace{-2mm}
\subsection{Garbage collection}

@@

This frees up both the memory allocated for the fiber stack as well as other
system resources, assuming that user code does not handle |Unwind| exception
and fails to re-raise it. But installing a finaliser on every captured
continuation by default introduces significant overhead to continuation
capture. Hence, we choose not to implement such a finaliser by default. It is
also useful to note that even if the memory for the fiber stack is managed by
the GC rather than being allocated in the C heap as we do now, we would still
need a finalisation mechanism to unwind the stack and release other system
resources that may be held by the continuation.

@@

>>>>

%\vspace{-2mm}
\subsection{Garbage collection}
\label{sec:gc}

@@

This frees up both the memory allocated for the fiber stack as well as other
system resources, assuming that user code does not handle |Unwind| exception
and fails to re-raise it. But installing a finaliser on every captured
continuation by default introduces significant overhead to continuation capture
(\S\ref{sec:res_final_k}). Hence, we choose not to implement such a finaliser by
default. It is also useful to note that even if the memory for the fiber stack
is managed by the GC rather than being allocated in the C heap as we do now, we
would still need a finalisation mechanism to unwind the stack and release other
system resources that may be held by the continuation.

@@

\subsubsection{Finalised continuations}
\label{sec:res_final_k}

In \S\ref{sec:gc}, we described how continuation resources can be cleaned up by
attaching a finaliser. Attaching this finaliser to every captured continuation
slows down generator (chameneos) benchmark by 4.1$\times$ (2.1$\times$)
compared to not attaching a finaliser. Hence, Multicore OCaml does not attach
such finaliser to every continuation by default.
